---
title: "The Names of Christ"
description: |
  Christ is called by at least 100 names in the scriptures. Christ is
  referred to in 41% of all Book of Mormon scriptures. Speakers in General 
  Conference speak of Christ at an accelerated rate. See
  who holds the record for the most references to Christ in a single talk.  
author:
  - name: Bryan Whiting
    url: https://www.bryanwhiting.com
date: 09-05-2021
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_depth: 3
categories:
   - general conference
   - scriptures
   - jesus christ
---


```{r setup, include=FALSE}
slug <- "the-names-of-christ" # basename(getwd())
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

```{r load}
here::i_am(fs::path('_posts', slug, slug, ext='Rmd'))
pkgs <- c("generalconference", "scriptuRs", "instaquote",
"dplyr", "gt", "tidytext", "DT", "reactable", "htmltools", "here")
for(p in pkgs) library(p, character.only = T)
source(here("R/ggtheme.R"), local = knitr::knit_global())
source(here("R/utils.R"), local = knitr::knit_global())

colors <- palette_pander(10)
# extrafont::loadfonts() ## to load the font
options(max.print = 1000)
data("genconf")
dfg <- genconf %>%
  unnest(sessions) %>%
  unnest(talks) %>%
  unnest(paragraphs) %>%
  mutate(
    paragraph2 = tolower(paragraph),
    date_str = date %>% format("%b %Y"),
    deep_link = glue("{url}.{p_id}?lang=eng#{p_id}"),
    p_href = glue('{author1} <a href="{deep_link}">{title1}</a>, {date_str}'),
    pquote = glue("{paragraph}<br>{p_href}"),
    # https://stackoverflow.com/a/26406796
    n_words = str_count(paragraph2, "\\S+")
  )

dfs <- lds_scriptures() %>%
  mutate(text2 = tolower(text))
```

## References to Christ in the Scriptures

A 1978 article by Susan Ward Easton, ["Names of Christ in the Book of Mormon"](https://abn.churchofjesuschrist.org/study/ensign/1978/07/discovery/names-of-christ-in-the-book-of-mormon?lang=eng), enumerated 100 names for the Savior. You can see those
listed here:

```{r name_table}
url <- "https://abn.churchofjesuschrist.org/study/ensign/1978/07/discovery/names-of-christ-in-the-book-of-mormon?lang=eng"
tabs <- rvest::read_html(url) %>% html_table()
df2 <- tabs[[2]]

names <- df2 %>%
  pull(Names) %>%
  str_replace("^[0-9]*\\.", "") %>%
  trimws() %>%
  head(100)
names_str <- paste(names, collapse = "|")

# Test: this is an overcounting
# str_count("Lord, the Lord of Hosts", "Lord|Lord of Hosts|Hosts")

df2 %>%
  head(100) %>%
  mutate(
    N = row_number(),
    Names = str_replace(Names, "^[0-9]*\\.", "") %>% trimws()
  ) %>%
  select(N, everything()) %>%
  reactable(
    defaultPageSize = 5,
    searchable = T,
    columns = list(
      N = colDef(minWidth = 40, header = "#")
    )
  )
# paged_table(df2)
```

Easton notes that there are 3,925 references to Christ in the Book of Mormon
based on these phrases. In this article, it was discovered there were at least 4,499 references to those same names^[It's possible that the author's analysis over counts some references that Easton excluded]. Comparing scriptures is interesting:

```{r scrip_cnts}
s_cnts <- dfs %>%
  mutate(cnt = str_count(text, names_str)) %>%
  select(volume_title, text, cnt)

s_cnts %>%
  mutate(at_least_one = cnt > 0) %>%
  group_by(volume_title) %>%
  summarize(
    n_verses = n(),
    cnt = sum(cnt),
    n_per_verse = cnt / n_verses,
    at_least_one = sum(at_least_one),
    pct_coverage = at_least_one / n_verses
  ) %>%
  gt() %>%
  cols_label(
    volume_title = "Scripture Volume",
    n_verses = "Verses in Volume",
    cnt = "# of References",
    at_least_one = "Verses",
    n_per_verse = "References Per Verse",
    pct_coverage = "% Verses"
  ) %>%
  tab_header(title = "References to Christ in the Scriptures") %>%
  summary_rows(
    columns = c(cnt, n_verses, at_least_one),
    fns = list(Total = "sum"),
    missing_text = "",
    decimals = 0
  ) %>%
  fmt_number(
    c(cnt, n_verses, at_least_one),
    decimals = 0
  ) %>%
  fmt_number(
    n_per_verse,
    decimals = 2
  ) %>%
  fmt_percent(pct_coverage, decimals = 0) %>%
  tab_spanner(
    label = "All References to Christ",
    columns = c(cnt, n_per_verse)
  ) %>%
  tab_spanner(
    label = "At Least One Reference",
    columns = c(at_least_one, pct_coverage)
  ) %>%
  tab_style(
    style = cell_borders(
      sides = "left",
      color = "#BBBBBB",
      weight = px(1.5),
      style = "solid"
    ),
    locations = cells_body(
      columns = c(cnt, at_least_one),
      rows = everything()
    )
  )
```

The Book of Mormon has more references to Christ than the other Testaments, but the Pearl of Great Price references the Savior the most.

How powerful that a whopping 41% of verses in the Book of Mormon refer to Christ! If you read just five verses, two of them are bound to inspire you to think of Him.

```{r quote, fig.width = 3, fig.height = 3, fig.align = 'center'}
text <- insta_text(
  "14,816",
  "The number of references to **Jesus Christ** in all the scriptures"
)
p <- instaquote(text)
photopost(
  p,
  caption = "Christ is referred to by 100 names in The Book of Mormon, which appear 4,500 times.",
  slug = slug,
  name = "names14k",
  quote=T
)
p
```

```{r}
text <- insta_text(
  "41%",
  "The % of verses that have at least one reference to **Jesus Christ** in all the scriptures",
)
p <- instaquote(text, bg_color = colors[2])
photopost(
  p,
  caption = "Nearly every other verse in the Book of Mormon refers to Christ.",
  slug = slug,
  name = "bofm_41pct",
  quote=T
)
```


## General Conference References to Christ

If we search for these same names of Christ as used in General
Conference talks, we see that each year, the leaders of the Church
speak of Christ thousands of times.

```{r gc_cnts}
g_cnts <- dfg %>%
  mutate(cnt = str_count(paragraph, names_str)) %>%
  select(paragraph, cnt, year) %>%
  group_by(year) %>%
  summarize(cnt = sum(cnt)) %>%
  filter(year <= 2020)

p <- g_cnts %>%
  ggplot(aes(x = year, y = cnt)) +
  geom_bar(stat = "identity", fill = colors[1]) +
  labs(
    title = 'Prophets speak of Christ',
    subtitle = custom_title(
      list(
        c("References to **Christ**", colors[1]),
        "in each year of conference"
      )
    ),
    y = ""
  ) +
  theme_ga 

photopost(
  p,
  caption = "Thousands...",
  slug = slug,
  name = "gc_cnts"
)
p
```

### Fraction of General Conference Words Referring to Christ

Are prophets speaking more of Christ? Each year, there are a different number of speakers and each talk is of a different length. In the 70's, General Conference had multiple sessions. If we divide the number of
words in a year by the number of references to Christ, we can see that
recently about 2.5% of all words spoken in conference are of Christ.

```{r pct_cnts}
names2 <- names %>%
  tibble() %>%
  filter(!(names %in% c("God", "Heavenly Father"))) %>%
  pull() %>%
  paste0(collapse = "|")

g_cnts <- dfg %>%
  mutate(
    cnt = str_count(paragraph, names2),
    at_least_one = cnt > 0
    ) %>%
  filter(year <= 2020) %>%
  group_by(year) %>%
  summarize(
    cnt = sum(cnt), 
    n_words = sum(n_words),
    n_paragraph = n(),
    at_least_one = sum(at_least_one)
    ) %>%
  mutate(
    pct_word = cnt/n_words,
    pct_para = at_least_one/n_paragraph
    )

p <- g_cnts %>%
  ggplot(aes(x = year, y = pct_word)) +
  geom_line(color = colors[1]) +
  geom_point(color = colors[1]) +
  geom_smooth(se=F, color=colors[2]) + 
  labs(
    title = 'Prophets are speaking more of Christ!',
    subtitle = custom_title(
      list(
        c("% of words referring to **Christ**", colors[1]),
        "in each year of conference, with",
        c("trend line.", colors[2])
      )
    ),
    y = ""
  ) +
  scale_y_continuous(labels = scales::percent, limits = c(0, .03)) + 
  theme_ga 
photopost(
  p,
  caption = "Prophets speak more of Christ now than ever",
  slug = slug,
  name = "pct_cnts"
)
p
```

### Percentage of General Conference Paragraphs Referring to Christ

To compare these numbers to the Book of Mormon, we computed the fraction of paragraphs in General Conference that speak of Christ. Remember, the Book of
Mormon refers to Christ in 41% of its verses. General Conference talks now refer more to Christ per paragraph than the other standard Works (except for the Pearl of Great Price, at 57% of verses.)

```{r plot_pct_paragraphs}
p <- g_cnts %>%
  ggplot(aes(x = year, y = pct_para)) +
  geom_line(color = colors[1]) +
  geom_point(color = colors[1]) +
  geom_smooth(se=F, color=colors[2]) + 
  labs(
    title = 'Prophets are speaking more of Christ!',
    subtitle = custom_title(
      list(
        c("% of paragraphs referring to **Christ**", colors[1]),
        "in each year <br>of conference with",
        c("trend line.", colors[2])
      )
    ),
    y = ""
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy=.1), limits = c(.30, .50)) + 
  theme_ga 
photopost(
  p,
  caption = "In 2020, 50% of paragraphs in General Conference talks referred to Christ",
  slug = slug,
  name = "pct_paragraphs"
)
p
```

## A Shift in the Trend

Prophets are speaking more of Christ than ever before, and at an accelerated rate.

In 2000, there was a 'break' in the trend compared to before, meaning that authors started referring to Christ more than ever before. Speakers continued to break the trend for several years until 2011 when the 'new trend' was set. See footnote for methods.
^[We use the `prophet` package in R, built by Facebook, which helps do "time series" modeling, or forecasting. Prophet is used to understand time series trends, and 
predicts the future based on averages in the past. It also has the ability to detect
what are called [changepoints](https://facebook.github.io/prophet/docs/trend_changepoints.html), or periods of time where the trends shift and experience a "new normal" if
you will.]
  

```{r prophet_changepoint}
library(prophet)
names2 <- names %>%
  tibble() %>%
  filter(!(names %in% c("God", "Heavenly Father"))) %>%
  pull() %>%
  paste0(collapse = "|")
g_cnts <- dfg %>%
  mutate(
    cnt = str_count(paragraph, names2),
    at_least_one = cnt > 0
    ) %>%
  group_by(date) %>%
  summarize(
    cnt = sum(cnt), 
    n_words = sum(n_words),
    n_paragraph = n(),
    at_least_one = sum(at_least_one)
    ) %>%
  mutate(
    pct_word = cnt/n_words,
    pct_para = at_least_one/n_paragraph
    )
# ggplot(g_cnts, aes(x = date, y = pct_word)) +
#   geom_point() +
#   geom_line() +
#   geom_smooth() +
#   labs(title = 'Trend by session in % of words spoken of Christ', y = "") +
#   scale_y_continuous(labels = scales::percent, limits = c(.01, .03)) +
#   theme_ga

tmp <- g_cnts %>% select(ds = date, y=pct_word)
# mod <- prophet(tmp, changepoint.range = )
mod <- prophet(tmp, changepoint.range = .8)
# forecast future sessions: https://facebook.github.io/prophet/docs/non-daily_data.html
future <- make_future_dataframe(mod, periods = 12*4, freq='month') %>%
  filter(str_detect(as.character(ds), '-04-|-10-'))
# tail(future)
forecast <- predict(mod, future)
# tail(forecast[c('ds', 'yhat', 'yhat_lower', 'yhat_upper')])

p <- plot(mod, forecast) + add_changepoints_to_plot(mod) + 
  labs(
    title = 'The shift to speaking more of Christ happend 2000-2010',
    subtitle = custom_title(
      list(
        "% of words referring to **Christ** in each session", 
        "<br>of conference with", 
        c("**forecast**", colors[1]),
        "and",
        c("**changepoints**", "red")
      )
    ),
    y = ""
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy=.1), limits = c(.01, .03)) + 
  theme_ga
p
photopost(
  p,
  caption = "Prophets are speaking of Christ at an accelerated rate each conference.
  
  In 2000, there was a 'break' in the trend compared to before, meaning that authors started referring to Christ more than ever before. Speakers continued to break the trend for several years until 2011 when the 'new trend' was set. 
  
  As you can see, prophets continue to speak more and more of Christ. The blue shade represents a 95% probability band, or in other words, we'd expect that, based on past data, there's a 95% chance that authors would speak of Christ, within this range.
  
  So in April 2020, the max expectation was that authors would refer to Christ 2.25% of
the time (top of blue band). In reality, they mentioned Him over 2.5% of every word.",
  slug = slug,
  name = "prophet_changepoint"
)
```

As you can see, prophets continue to speak more and more of Christ. The blue shade represents a 95% probability band, or in other words, we'd expect that, based on past data, there's a 95% chance that authors would speak of Christ, within this range.
  
So in April 2020, the max expectation was that authors would refer to Christ 2.25% of
the time (top of blue band). In reality, they mentioned Him over 2.5% of every word.


### Top 20 talks Referring to Christ

A Dallin H Oak talk in the 70's spoke of Christ 139 times. Check out the 20 talks
that speak the most of Christ.^[Note: The text parser used in this analysis
would search for "Jesus" and "Christ" separately, so "Jesus Christ" would
count as two references.]

```{r top_talks}
pure_names = c("Savior|Jesus|Christ")
# str_count("Jesus Christ", pure_names)
x <- dfg %>%
  mutate(
    cnt = str_count(paragraph, names2),
    jesus_only = str_count(paragraph, pure_names)
    ) %>%
  group_by(title1, author1, date_str, url) %>%
  summarize(
    cnt = sum(cnt),
    jesus_only = sum(jesus_only)) %>%
  ungroup() %>%
  arrange(desc(cnt)) %>%
  mutate(title1 = glue('{author1}, <a href="{url}">{title1}</a>, {date_str}')) %>%
  select(title1, cnt, jesus_only) %>%
  head(20)

datatable(
  x, escape = F,
  colnames = c("Talk", "All References to Christ", "References to Savior, Jesus, or Christ")
)
```


# Closing

President Nelson's [Hear Him](https://www.churchofjesuschrist.org/study/general-conference/2020/04/45nelson?lang=eng) talk in April 2020 referenced Christ 70 times (ranked 7th out of top 20).

Is it a wonder why Christ is being spoken of more by the Prophets?

> And we talk of Christ, we rejoice in Christ, we preach of Christ, we prophesy of Christ, and we write according to our prophecies, that our children may know to what source they may look for a remission of their sins. [2 Nephi 25:26](https://www.churchofjesuschrist.org/study/scriptures/bofm/2-ne/25.26?lang=eng#p25)
