---
title: "The Names of Christ"
description: |
  Christ is called by at least 100 names in the scriptures.
author:
  - name: Bryan Whiting
    url: https://www.bryanwhiting.com
date: 09-05-2021
slug: christ
output:
  distill::distill_article:
    self_contained: false
categories:
   - general conference
   - scriptures
   - jesus christ
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
slug <- "the-names-of-christ" # basename(getwd())
```

```{r load}
library(generalconference)
library(scriptuRs)
library(dplyr)
library(gt)
library(tidytext)
library(ggplot2)
library(instaquote)
# library(rmarkdown)
library(DT)
library(reactable)
library(htmltools)
source("/home/rstudio/gospel_analysis_blog/R/ggtheme.R")
source("/home/rstudio/gospel_analysis_blog/R/utils.R")

colors <- palette_pander(10)
# extrafont::loadfonts() ## to load the font
options(max.print = 1000)
data("genconf")
dfg <- genconf %>%
  unnest(sessions) %>%
  unnest(talks) %>%
  unnest(paragraphs) %>%
  mutate(
    paragraph2 = tolower(paragraph),
    date_str = date %>% format("%b %Y"),
    deep_link = glue("{url}.{p_id}?lang=eng#{p_id}"),
    p_href = glue('{author1} <a href="{deep_link}">{title1}</a>, {date_str}'),
    pquote = glue("{paragraph}<br>{p_href}"),
    # https://stackoverflow.com/a/26406796
    n_words = str_count(paragraph2, "\\S+")
  )

dfs <- lds_scriptures() %>%
  mutate(text2 = tolower(text))
```

A 1978 article by Susan Ward Easton, ["Names of Christ in the Book of Mormon"](https://abn.churchofjesuschrist.org/study/ensign/1978/07/discovery/names-of-christ-in-the-book-of-mormon?lang=eng), enumerated 100 names for the Savior. You can see those
listed here:

```{r name_table}
url <- "https://abn.churchofjesuschrist.org/study/ensign/1978/07/discovery/names-of-christ-in-the-book-of-mormon?lang=eng"
tabs <- rvest::read_html(url) %>% html_table()
df2 <- tabs[[2]]

names <- df2 %>%
  pull(Names) %>%
  str_replace("^[0-9]*\\.", "") %>%
  trimws() %>%
  head(100)
names_str <- paste(names, collapse = "|")

# Test: this is an overcounting
# str_count("Lord, the Lord of Hosts", "Lord|Lord of Hosts|Hosts")


df2 %>%
  head(100) %>%
  mutate(
    N = row_number(),
    Names = str_replace(Names, "^[0-9]*\\.", "") %>% trimws()
  ) %>%
  select(N, everything()) %>%
  reactable(
    defaultPageSize = 5,
    searchable = T,
    columns = list(
      N = colDef(minWidth = 40, header = "#")
    )
  )
# paged_table(df2)
```

Easton notes that there are 3,925 references to Christ in the Book of Mormon
based on these phrases. In this article, it was discovered there were at least 4,499 references to those same names^[It's possible that the author's analysis over counts some references that Easton excluded]. Comparing scriptures is interesting:

```{r scrip_cnts}
s_cnts <- dfs %>%
  mutate(cnt = str_count(text, names_str)) %>%
  select(volume_title, text, cnt)

s_cnts %>%
  mutate(at_least_one = cnt > 0) %>%
  group_by(volume_title) %>%
  summarize(
    n_verses = n(),
    cnt = sum(cnt),
    n_per_verse = cnt / n_verses,
    at_least_one = sum(at_least_one),
    pct_coverage = at_least_one / n_verses
  ) %>%
  gt() %>%
  cols_label(
    volume_title = "Scripture Volume",
    n_verses = "Verses in Volume",
    cnt = "# of References",
    at_least_one = "Verses",
    n_per_verse = "References Per Verse",
    pct_coverage = "% Verses"
  ) %>%
  tab_header(title = "References to Christ in the Scriptures") %>%
  summary_rows(
    columns = c(cnt, n_verses, at_least_one),
    fns = list(Total = "sum"),
    missing_text = "",
    decimals = 0
  ) %>%
  fmt_number(
    c(cnt, n_verses, at_least_one),
    decimals = 0
  ) %>%
  fmt_number(
    n_per_verse,
    decimals = 2
  ) %>%
  fmt_percent(pct_coverage, decimals = 0) %>%
  tab_spanner(
    label = "All References to Christ",
    columns = c(cnt, n_per_verse)
  ) %>%
  tab_spanner(
    label = "At Least One Reference",
    columns = c(at_least_one, pct_coverage)
  ) %>%
  tab_style(
    style = cell_borders(
      sides = "left",
      color = "#BBBBBB",
      weight = px(1.5),
      style = "solid"
    ),
    locations = cells_body(
      columns = c(cnt, at_least_one),
      rows = everything()
    )
  )
```

The Book of Mormon has more references to Christ than the other Testaments, but the Pearl of Great Price references the Savior the most.

How powerful that a whopping 41% of verses in the Book of Mormon refer to Christ! If you read just five verses, two of them are bound to inspire you to think of Him.

```{r quote, fig.width = 3, fig.height = 3, fig.align = 'center'}
text <- insta_text(
  "14,816",
  "The number of references to **Jesus Christ** in all the scriptures"
)
p <- instaquote(text)
photopost(
  p,
  caption = "Christ is referred to by 100 names in The Book of Mormon, which appear 4,500 times.",
  slug = slug,
  name = "names14k"
)
p
```

## General Conference References to Christ

If we search for these same names of Christ as used in General
Conference talks, we see that each year, the leaders of the Church
speak of Christ thousands of times.

```{r gc_cnts}
g_cnts <- dfg %>%
  mutate(cnt = str_count(paragraph, names_str)) %>%
  select(paragraph, cnt, year) %>%
  group_by(year) %>%
  summarize(cnt = sum(cnt)) %>%
  filter(year <= 2020)

p <- g_cnts %>%
  ggplot(aes(x = year, y = cnt)) +
  geom_bar(stat = "identity", fill = colors[1]) +
  labs(
    title = 'Prophets speak of Christ',
    subtitle = custom_title(
      list(
        c("References to **Christ**", colors[1]),
        "in each year of conference"
      )
    ),
    y = ""
  ) +
  theme_ga 

photopost(
  p,
  caption = "Thousands...",
  slug = slug,
  name = "gc_cnts"
)
p
```

Are prophets speaking more of Christ? Each year, there are a different number of speakers and each talk is of a different length. In the 70's, General Conference had multiple sessions. If we divide the number of
words in a year by the number of references to Christ, we can see that
recently, about 3% of all words spoken in conference are of Christ.

```{r pct_cnts}
g_cnts <- dfg %>%
  mutate(cnt = str_count(paragraph, names_str)) %>%
  filter(year <= 2020) %>%
  group_by(year) %>%
  summarize(
    n_paragraph = n(),
    cnt = sum(cnt), 
    n_words = sum(n_words)) %>%
  mutate(pct = cnt/n_words)

p <- g_cnts %>%
  ggplot(aes(x = year, y = pct)) +
  geom_line(color = colors[1]) +
  geom_point(color = colors[1]) +
  labs(
    title = 'Prophets are speaking more of Christ!',
    subtitle = custom_title(
      list(
        c("References to **Christ**", colors[1]),
        "in each year of conference"
      )
    ),
    y = ""
  ) +
  scale_y_continuous(labels = scales::percent, limits = c(0, .03)) + 
  theme_ga 
photopost(
  p,
  caption = "Prophets speak more of Christ now than ever",
  slug = slug,
  name = "pct_cnts"
)
p
```

One talk in the 70's spoke of Christ 182 times. Check out the talks
that speak the most of Christ.

```{r}
x <- dfg %>%
  mutate(cnt = str_count(paragraph, names_str)) %>%
  group_by(title1, author1, date_str, url) %>%
  summarize(cnt = sum(cnt)) %>%
  arrange(desc(cnt)) %>%
  mutate(url = glue('<a href="{url}">link</a>')) %>%
  select(title1, author1, date_str, url, cnt) %>%
  head(100)

datatable(
  x, escape = F
)
```

