---
title: "The Names of Christ"
description: |
  Christ is called by at least 100 names in the scriptures.
author:
  - name: Bryan Whiting
    url: https://www.bryanwhiting.com
date: 09-05-2021
slug: christ
output:
  distill::distill_article:
    self_contained: false
categories:
   - general conference
   - scriptures
   - jesus christ
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load}
library(generalconference)
library(scriptuRs)
library(dplyr)
library(gt)
library(tidytext)
library(ggplot2)
library(instaquote)
# library(rmarkdown)
library(DT)
library(reactable)
library(htmltools)
source("/home/rstudio/gospel_analysis_blog/_posts/ggtheme.R")
source("/home/rstudio/gospel_analysis_blog/_posts/utils.R")

colors <- palette_pander(10)
# extrafont::loadfonts() ## to load the font
options(max.print = 1000)
data("genconf")
dfg <- genconf %>%
  unnest(sessions) %>%
  unnest(talks) %>%
  unnest(paragraphs) %>%
  mutate(
    paragraph2 = tolower(paragraph),
    date_str = date %>% format("%b %Y"),
    deep_link = glue("{url}.{p_id}?lang=eng#{p_id}"),
    p_href = glue('{author1} <a href="{deep_link}">{title1}</a>, {date_str}'),
    pquote = glue("{paragraph}<br>{p_href}")
  )

dfs <- lds_scriptures() %>%
  mutate(text2 = tolower(text))
```

A 1978 article by Susan Ward Easton, ["Names of Christ in the Book of Mormon"](https://abn.churchofjesuschrist.org/study/ensign/1978/07/discovery/names-of-christ-in-the-book-of-mormon?lang=eng), enumerated 100 names for the Savior. You can see those
listed here:

```{r name_table}
url <- "https://abn.churchofjesuschrist.org/study/ensign/1978/07/discovery/names-of-christ-in-the-book-of-mormon?lang=eng"
tabs <- rvest::read_html(url) %>% html_table()
df2 <- tabs[[2]] 

names <- df2 %>%
  pull(Names) %>%
  str_replace("^[0-9]*\\.", "") %>%
  trimws() %>%
  head(100)
names_str <- paste(names, collapse = "|")

df2 %>%
  head(100) %>%
  mutate(
    N = row_number(),
    Names = str_replace(Names, "^[0-9]*\\.", "") %>% trimws()
    ) %>%
  select(N, everything()) %>%
  reactable(
    defaultPageSize=5,
    searchable=T,
    columns= list(
      N = colDef(minWidth = 40, header="#")
    ))
# paged_table(df2)
```

Easton notes that there are 3,925 references to Christ in the Book of Mormon
based on these phrases. In this article, it was discovered there were at least 4,499 references to those same names^[It's possible that the author's analysis over counts some references that Easton excluded]. Comparing scriptures is interesting:

```{r scrip_cnts}
s_cnts <- dfs %>%
  mutate(cnt = str_count(text, names_str)) %>%
  select(volume_title, text, cnt) 

s_cnts %>%
  mutate(at_least_one = cnt > 0) %>%
  group_by(volume_title) %>%
  summarize(
    n_verses = n(),
    cnt = sum(cnt),
    n_per_verse = cnt/n_verses,
    at_least_one = sum(at_least_one),
    pct_coverage = at_least_one/n_verses
    ) %>%
  gt() %>%
  cols_label(
    volume_title = "Scripture Volume",
    n_verses = "Verses in Volume",
    cnt = "# of References",
    at_least_one = "Verses",
    n_per_verse = "References Per Verse",
    pct_coverage = "% Verses"
  ) %>%
  tab_header(title = "References to Christ in the Scriptures") %>%
  summary_rows(columns=c(cnt, n_verses, at_least_one),
    fns = list(Total="sum"),
    missing_text = "",
    decimals=0) %>%
  fmt_number(
    c(cnt, n_verses, at_least_one),
    decimals=0) %>%
  fmt_number(
    n_per_verse, decimals = 2
  ) %>%
  fmt_percent(pct_coverage, decimals=0) %>%
  tab_spanner(
    label = "All References to Christ",
    columns = c(cnt, n_per_verse)
  ) %>%
  tab_spanner(
    label = "At Least One Reference",
    columns = c(at_least_one, pct_coverage)
  ) %>%
  tab_style(
    style = cell_borders(
      sides = "left",
              color = "#BBBBBB",
        weight = px(1.5),
        style = "solid"
    ),
    locations = cells_body(
      columns = c(cnt, at_least_one),
      rows = everything()
    )
  )
```

The Book of Mormon has more references to Christ than the other Testaments, but the Pearl of Great Price references the Savior the most.

How powerful that a whopping 41% of verses in the Book of Mormon refer to Christ! If you read just five verses, two of them are bound to inspire you to think of Him.

```{r quote, fig.width = 3, fig.height = 3, fig.align = 'center'}
text <- insta_text(
  '14,816',
  'The number of references to **Jesus Christ** in all the scriptures'
)
instaquote(text) 
```

```{r gc_cnts}
g_cnts <- dfg %>%
  mutate(cnt = str_count(paragraph, names_str)) %>%
  select(paragraph, cnt, year)

```



