---
title: "Second Coming of Jesus Christ"
description: |
  While the phrase "second coming" isn't used often in the scriptures,
  other phrases are. Interestingly, there's a spike in the invitation 
  to "hear Him", perhaps commonly seen on social media as #hearhim.
author:
  - name: Bryan Whiting
    url: https://www.bryanwhiting.com
date: 09-03-2021
output:
  distill::distill_article:
    self_contained: false
categories:
   - general conference
   - scriptures
   - second coming
   - jesus christ
   - hear him
   - word trends
---


```{r setup, include=FALSE}
slug = 'second-coming'
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
# slug <- #basename(getwd())
```


```{r}
here::i_am(fs::path("_posts", slug, slug, ext = "Rmd"))
pkgs <- c(
  "generalconference", "scriptuRs", "instaquote",
  "dplyr", "gt", "tidytext", "DT", "reactable", "htmltools", "here"
)
for (p in pkgs) library(p, character.only = T)
source(here("R/ggtheme.R"), local = knitr::knit_global())
source(here("R/utils.R"), local = knitr::knit_global())
source(here("R/social_media.R"), local = knitr::knit_global())

colors <- palette_pander(10)
# extrafont::loadfonts() ## to load the font
options(max.print = 1000)
data("genconf")
dfg <- genconf %>%
  unnest(sessions) %>%
  unnest(talks) %>%
  unnest(paragraphs) %>%
  mutate(
    paragraph2 = tolower(paragraph),
    date_str = date %>% format("%b %Y"),
    deep_link = glue("{url}.{p_id}?lang=eng#{p_id}"),
    p_href = glue('{author1} <a href="{deep_link}">{title1}</a>, {date_str}'),
    pquote = glue("{paragraph}<br>{p_href}")
  )

dfs <- lds_scriptures() %>%
  mutate(text2 = tolower(text))
```

Disciples of Christ eagerly await His return to the earth, commonly known as the "Second Coming". But where does this phrase come from, and how is it being used today?

## Usage of "Second Coming" in Text

The exact phrase "second coming" is only mentioned once in all of the scriptures:

```{r, results="asis"}
dfs %>%
  filter(str_detect(text2, "second coming")) %>%
  quote_verse("second coming")
```

Yet the phrase is mentioned often in General Conference. It was mentioned a lot in the mid 70's, but seems to be picking back up again.

```{r}
cnt <- dfg %>%
  filter(str_detect(paragraph2, "second coming")) %>%
  count(year)
# View(cnt)
p <- cnt %>%
  ggplot(aes(x = year, y = n)) +
  geom_bar(stat = "identity", fill = colors[1]) +
  labs(
    title = 'Number of References to "Second Coming" By Year',
    subtitle = custom_title(
      list(
        c("Recent trend", colors[2]),
        "of",
        c("references to **second coming**", colors[1])
      )
    ),
    y = ""
  ) +
  geom_smooth(se = F, color = colors[2]) +
  theme_ga

make_post(
  img = p,
  title = "References to Christ's second coming have revived",
  body = "",
  slug = slug,
  name = 'gg_second_coming',
  is_quote = F
)
p 
```



## Other Mentions of "Second Coming"

Turns out that the authors in the Scriptures just referred to the Savior's
Second Coming in a different way. Looking at the 
[Gospel Topics: Second Coming](https://www.churchofjesuschrist.org/study/manual/gospel-topics/second-coming-of-jesus-christ?lang=eng), 
[Topical Guide: Jesus Christ, Second Coming](https://www.churchofjesuschrist.org/study/scriptures/tg/jesus-christ-second-coming?lang=eng), and the 
[Index to the Triple Combination: Jesus Christ, Second Coming of](https://www.churchofjesuschrist.org/study/scriptures/triple-index/jesus-christ-second-coming-of?lang=eng), there are a few other phrases used to refer to His coming.

> They that are wise and have received the truth, and have taken the Holy Spirit for their guide, and have not been deceived—verily I say unto you, they shall not be hewn down and cast into the fire, but shall abide the day....For the **Lord shall be in their midst**, and his glory shall be upon them, and he will be their king and their lawgiver. [D&C 45:57-59](https://www.churchofjesuschrist.org/study/scriptures/dc-testament/dc/45.57-59?lang=eng#p57)

> The hour and the day no man knoweth, neither the angels in heaven, nor shall they know until **he comes**. [D&C 49:7](https://www.churchofjesuschrist.org/study/scriptures/dc-testament/dc/49.7?lang=eng#p7).

> King of glory **shall come**... [Ps 24:7](https://www.churchofjesuschrist.org/study/scriptures/ot/ps/24.7?lang=eng#p7)

> they that are Christ’s **at his coming**... [1 Cor 15:23](https://www.churchofjesuschrist.org/study/scriptures/nt/1-cor/15.23?lang=eng#p23)

If we use these and phrases to search for His coming, we'd see a lot more 
references.

## Preparing for His Coming by Hearing Him

The Lord teaches us that those who are prepared for His coming "have taken the Holy Spirit for their guide" ([D&C 45:57-59](https://www.churchofjesuschrist.org/study/scriptures/dc-testament/dc/45.57-59?lang=eng#p57)) and warns that those
"that will not hear my voice, the same shall ye not receive into my church, for [those] I will not receive at the last day."
([Mosiah 26:28](https://www.churchofjesuschrist.org/study/scriptures/bofm/mosiah/26?lang=eng))

This phrase "ye not receive" is not exclusive (as if the followers of Christ
are better than non-followers) because Christ "inviteth them all to come unto him and partake of his goodness" (2 Ne. 26:33). It's a qualification for baptism, i.e., reception into His church. Individuals need to demonstrate they've "are willing to take upon them the name of Jesus Christ" ([D&C 20:37](https://www.churchofjesuschrist.org/study/scriptures/dc-testament/dc/20.p37?lang=eng#p36)), and follow him. 

The calls to "Hear Him" are abundant in General Conference talks. Here are 20
We can see the 20 most recent references to "Hear Him":

```{r, layout="l-body-outset"}
dfg %>%
  filter(str_detect(paragraph2, "hear him")) %>%
  datatable_quotes(n = 20, c('hear Him', 'hear him', 'Hear Him'))
```

## "Hear Him" is Trending in Conference

This phrase has recently spiked.


```{r}
cnt <- dfg %>%
  filter(str_detect(paragraph2, "hear him")) %>%
  group_by(year) %>%
  count()

# View(cnt)
p <- cnt %>%
  ggplot(aes(x = year, y = n)) +
  geom_bar(stat = "identity", fill = colors[1]) +
  # scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by=5))
  geom_smooth(se = F, color = colors[2]) +
  theme_ga + 
  labs(
    title = "There were 28 prophetic invitations to **Hear Him** in 2020",
    subtitle = custom_title(list(
      c("Recent trend", colors[2]),
      "of",
      c("calls to **hear him**", colors[1]),
      "by year"
    )),
    caption = "*2021 is only halfway over\ngospelanalysis.com",
    y = ""
  )

make_post(
  img = p,
  title = "2020 had a theme to 'Hear Him'",
  body = "It's not uncommon for prophets to invite us to #hearhim. But recently, there's been a surge in the phrase. Perhaps this suggests how important it is to learn to hear the Lord. Perhaps it also reflects that the prophets share their talks and co-inspire given themes.",
  slug = slug,
  name = 'gg_hear_him',
  is_quote = F
)
p
```
```{r eval=F}
p <- instaquote(
  title = "'Hear Him' was mentioned **28** times in General Conference in 2020",
  subtitle = NULL,
  bg_color = colors[5]
)
make_post(
  img = p,
  title = "28!",
  body = "",
  slug = slug,
  name = 'iq_28',
  is_quote = T
)

```


So, how will you prepare for His second coming? Perhaps a good place to start
is to practice [hearing Him](https://www.churchofjesuschrist.org/study/general-conference/2020/04/45nelson?lang=eng.).
