---
title: "Learning Truth form Prophets"
description: |
  "Wherefore, we search the prophets" - Jacob 4:6.
author:
  - name: Bryan Whiting
    url: https://www.bryanwhiting.com
date: 2021-10-02
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_depth: 3
categories:
   - scriptures
   - prophets
---


```{r setup, include=FALSE}
slug <- "prophets" # basename(getwd())
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```


```{r load}
here::i_am(fs::path("_posts", slug, slug, ext = "Rmd"))
pkgs <- c(
  "generalconference", "scriptuRs", "instaquote",
  "dplyr", "gt", "tidytext", "DT", "reactable", "htmltools", "here"
)
for (p in pkgs) library(p, character.only = T)
source(here("R/ggtheme.R"), local = knitr::knit_global())
source(here("R/utils.R"), local = knitr::knit_global())
source(here("R/social_media.R"), local = knitr::knit_global())

colors <- palette_pander(10)
# extrafont::loadfonts() ## to load the font
options(max.print = 1000)
data("genconf")
dfg <- genconf %>%
  unnest(sessions) %>%
  unnest(talks) %>%
  unnest(paragraphs) %>%
  mutate(
    paragraph2 = tolower(paragraph),
    date_str = date %>% format("%b %Y"),
    deep_link = glue("{url}.{p_id}?lang=eng#{p_id}"),
    p_href = glue('{author1} <a href="{deep_link}">{title1}</a>, {date_str}'),
    pquote = glue("{paragraph}<br>{p_href}"),
    # https://stackoverflow.com/a/26406796
    n_words = str_count(paragraph2, "\\S+")
  )

dfs <- lds_scriptures() %>%
  mutate(text2 = tolower(text))
```

```{r}
p <- instaquote(
  title = "We search the prophets",
  subtitle = "Jacob 4\\:6"
)
make_post(
  img = p,
  title = "How do you search the prophets?",
  body = "I've been pondering this powerful phrase, and the more I do, the more I come to appreciate the Lord's constant invitation to search, ask, and find.
  
  Disciples of Christ are those who seek. Yearn for truth. Not just in religious matters, but all matters.",
  slug=slug,
  name='jacob4_6',
  is_quote=TRUE
)
p
```

I've been pondering this powerful phrase; the more I do, the more I come to appreciate the Lord's constant invitation to search, ask, and find.

Disciples of Christ are those who seek. Who yearn for truth. Not just in religious matters but all matters.

Jacob continues his discourse with another compelling insight:

```{r}
p <- instaquote(
  title = "No man knoweth of his ways save it be revealed unto him",
  subtitle = "Jacob 4:8",
  bg_color = colors[2]
)
make_post(
  img = p,
  title = "There's only one way to know God.",
  body = "And by the power of the Holy Ghost ye may know the truth of all things. Moroni 10:4-5",
  slug = slug,
  name = 'jacob4_8',
  is_quote=TRUE
)
p
```

How powerful: the only way to know His ways is by revelation. Moroni echos this testimony:

> And by the power of the Holy Ghost ye may know the truth of all things. [Moroni 10:4-5](https://www.churchofjesuschrist.org/study/scriptures/bofm/moro/10?lang=eng)

How have you come to know God?